\documentclass{letter}
\usepackage{hyperref}
% Palatino for rm and math | Helvetica for ss | Courier for tt
\usepackage{mathpazo} % math & rm
\linespread{1.05}        % Palatino needs more leading (space between lines)
\usepackage[scaled]{helvet} % ss
\usepackage{courier} % tt
\normalfont
\usepackage[T1]{fontenc}

\usepackage[a4paper,left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}

\newcounter{section}
\newcounter{subsection}[section]
\setcounter{secnumdepth}{3}
\makeatletter
\newcommand\section{\@startsection {section}{1}{\z@}%
                                   {-3.5ex \@plus -1ex \@minus -.2ex}%
                                   {2.3ex \@plus.2ex}%
                                   {\normalfont\Large\bfseries}}
\newcommand\subsection{\@startsection{subsection}{2}{\z@}%
                                     {-3.25ex\@plus -1ex \@minus -.2ex}%
                                     {1.5ex \@plus .2ex}%
                                     {\normalfont\large\bfseries}}
\renewcommand \thesection{\@arabic\c@section}
\renewcommand\thesubsection{\thesection.\@arabic\c@subsection}

\makeatletter
\renewcommand{\closing}[1]{\par\nobreak\vspace{\parskip}%
  \stopbreaks
  \noindent
  \ifx\@empty\fromaddress\else
  \hspace*{\longindentation}\fi
  \parbox{\indentedwidth}{\raggedright
       \ignorespaces #1\\[2\medskipamount]%
       \ifx\@empty\fromsig
           \fromname
       \else \fromsig \fi\strut}%
   \par}
\makeatother

\signature{Devavrat V. Dabke \qquad Eva E. Arroyo}
\address{Duke University \\
Campus Box 98900 \\
Durham, NC 27708}

\longindentation=0pt

\begin{document}

\begin{letter}{Professor\ John Carter\\
Associate Editor\\
SIAM Undergraduate Research Online\\}
\opening{To Professor\ Carter:}

We are resubmitting our paper ``Rumors with Personality: Differential and Agent-Based Models of Information Spread through Networks'' by Devavrat V. Dabke and Eva E. Arroyo for your consideration.
We would like to thank the reviewers for their comments and have revised our draft accordingly.

Overall, we continue with the same three models as in the previous draft, but with clarifications on their similarities and differences, as well as on our choice of parameters for each.
Because of the confusion in introducing the ISTK model itself---originally just a set of four equations---we added a new flowchart and restructured the section (Section 1.3).
We feel these steps greatly clarify the way in which populations move within our model.
To better explain our results, we updated several figures, and rewrote more precise descriptions of our data.
Finally, the conclusion better describes how individual feature vectors relate to the spread of the rumor throughout the population.

Below, we provide detailed reference to each of the comments left to us by the reviewers.
We greatly appreciate the feedback we received, and we feel that our manuscript has improved because of it.

Please let us know if there are any more questions or comments concerning our paper.

\vspace{12pt}
\closing{Sincerely,}

\section{Response to Reviewer 1}
\input{rev1-part1}
\input{rev1-part2}

\section{Response to Reviewer 2}
\input{rev2-intro}
\input{rev2-1.2}
\input{rev2-1.3}
\input{rev2-2.1}
\input{rev2-2.2}
\input{rev2-3.1}
\input{rev2-3.2}
\input{rev2-results-discussion}
\input{rev2-end}

\end{letter}
\end{document}
