\subsection{Part 2: General Recommendations}
\textbf{Comment} \\
It is my opinion that the manuscript ``Rumors with Personality,'' by Dabke and Arroyo (supervised by Layton) is of sufficient quality and interest for publication in SIURO.
While I've found no flaws in the manuscript that warrant major revision, I'd like to make some suggestions for points to make in the conclusion.
The authors point out that the richest and least trivial dynamical behavior seems to be present in agent based models with feature vectors that describe both agents and rumors.
These models, in many instances, exhibit rumors that die out before all members of the network (even if it is fully connected) observe it.
The authors already speculate that it might be possible to engineer a perfect rumor that will fully saturate the network.
It's not clear to me if this engineering would be more dependent upon the feature vectors of the agents in the network or upon the topology and architecture of the network itself.
Some clarification (or at least mention) of this might be helpful.
In any case, other questions for future study that might be of equal interest would be is it possible to design a network topology that is somehow not so restrictive that it still allows agents to interact in ways the people expect of social networks yet it also effectively dampens the spread of as many rumors as possible.
Likewise, would it be possible for an agent within a network to engineer their own feature vector (even if it means lying about their personal attributes when creating their account) in a way that inoculates them against the spread of a majority (or at least a plurality) of the prevailing rumors.

\textbf{Response} \\
The new final paragraph in our discussion addresses this suggestion.
Essentially, we consider both how the characteristics of the individuals and the rumor affects the spread, as well as the network topology.
Additionally, we would like to note that we assume that our data was representative of a ``true'' set of features for an individual.
The modeling of dishonesty and lying is compelling, and it is something that we would like to consider for the future.
Moreover, each feature in the characteristic vector for an individual represents something to which they would positively respond; in that if they had a coding for ``English'' as a language they spoke, then a rumor with the corresponding feature ``English'' would appeal to them.
However, it is possible that an individual is very interested in ``French'' and a feature corresponding to ``French'' in a vector would also cause them to be more likely to spread the rumor.
The features we pulled from the dataset provided a reasonable set of data to generate feature vectors.
However, we would like to note that the underlying assumption we make is that it \textit{is} possible to find feature vectors which map to how an individual might respond more positively to corresponding features in a ``rumor.''
We have clarified this idea in our introduction and discussion.
