\subsection{Section 3.1}
\newcounter{rev2-3.1}
\setcounter{rev2-3.1}{1}

\textbf{Comment \arabic{rev2-3.1}} \\
You say ``Facebook differential model''.
It's not clear what you mean by this.
Is it the ISTK model or something else?

\textbf{Response \arabic{rev2-3.1}} \\
We specifically changed this to simply say ``the differential model.''
As mentioned in our responses to the comments for Section 1.3, we have addressed our sloppy references to the three models by enforcing a consistent naming scheme.
\stepcounter{rev2-3.1}

\textbf{Comment \arabic{rev2-3.1}} \\
Because I'm not sure what the Facebook differential model is, I'm not sure exactly what you have done.
It appears that either (1) you have run the ISTK model with some parameters the you estimated from Facebook or (2) you collected data from Facebook.

\textbf{Response \arabic{rev2-3.1}} \\
All three models are versions of the ISTK model.
Again, we worked on keeping our names for the three models consistent throughout the paper.
In addition, we have clarified the relationship between the differential model and the simple, agent-based one with the first paragraph of this section.
\stepcounter{rev2-3.1}

\textbf{Comment \arabic{rev2-3.1}} \\
I'm guessing an agent-based model is relatively standard.
If so, a reference for this would be quite helpful.

\textbf{Response \arabic{rev2-3.1}} \\
We have added a reference for generally using agent-based models for stochastic network dynamics.
Specifically, this is Reference 23: ``T. A. Snijders''.
\stepcounter{rev2-3.1}
