\subsection{Introductory Comments}
\newcounter{rev2-intro}
\setcounter{rev2-intro}{1}

\textbf{Comment \arabic{rev2-intro}} \\
Overall, in the current state of the paper, I do not recommend the paper for publication.
There are two main issues:

\textbf{Response \arabic{rev2-intro}} \\
We believe that we have corrected and addressed the issues that were outlined.
\stepcounter{rev2-intro}

\textbf{Comment \arabic{rev2-intro}} \\
It appears that this paper tries to accomplish too much.
There seem to be 3 models, none of which are explored much in depth and not enough is said about comparisons between them.

\textbf{Response \arabic{rev2-intro}} \\
Throughout the paper we have tried to make clearer that the three models form a progression, and are based on the same model: the ITSK model.
The differential ISTK model provides a baseline for our model by demonstrating rumor spread over a homogenous, generalized population.
The simple, agent-based ISTK model introduces more complexity, particularly that of a network.
With the agent-based setup, we gain more control over the model and can take into account the rumor's spread over the specific network structure provided to us by our Facebook dataset.
Finally, we arrive at the feature-vector, agent-based ISTK model which allows us to track the ``personality'' of a rumor as it spreads through the network.
We can take into account the demographic information over the population (again, by using our Facebook dataset), in addition to the network.

The entire paper demonstrates how including a network and a ``personality'' changes the way a rumor spreads.
Our introduction has been modified to clarify this progression and unify the three versions of the ISTK model.
We also have standardized that names we use for these three different versions of the ISTK model throughout the paper, so as to further demonstrate their core connection.
\stepcounter{rev2-intro}

\textbf{Comment \arabic{rev2-intro}} \\
Because of the first issue, there is not enough detail in the models.
For example, in the ISTK differential equation model, results are shown, however there is not sufficient detail in all of the choices of parameters to reproduce the results.
I believe this is true about all of the models.

\textbf{Response \arabic{rev2-intro}} \\
We have revised the introduction, including major revisions of Section 1.3 that includes a flow chart to better express our model.
We made the language in Sections 2 and 3 more precise, so as to better communicate the specific workings on each model.
Section 2.2.2 has been updated to clarify the parameter choice for the differential equation.
Section 3.1 has been updated to clarify the parameter choice for the simple, agent-based model.
Section 3.1 has been updated to clarify the parameter choice for the feature-vector, agent-based model.
\stepcounter{rev2-intro}
